Hierarchical wrinkling in a confined permeable biogel

### 2015-01-22 fig_plis/article_plis.tex
transition au début de Models and scaling laws et résumé à la fin

\seb{\it Ajouter une transition: en l'etat le passage au modele est trop brutal.}

@@

% Pour Mathieu : ajouter quelque part des applications numériques pour les trois longueurs d'ondes gravité, Darcy, Poiseuille
We identify three possible candidates for the transverse load $\sigma_\perp$: the weight or buoyancy of the gel, the porous flow through the gel or the viscous flows in the surrounding water layers. We confirmed that the former plays no significant role by successfully repeating our experiment in a cell held vertically, i.e. with the weight acting longitudinally rather than transversely.

@@

\seb{\it Resumer ce qui precede en une phrase disant dans quel domaine de longueur d'onde on s'attend a trouver quel scaling pour nos manips.}

@@

Our results are displayed in Fig.~\ref{fig:DarcyPoiseuille}. Although they provide the correct order of magnitude for $\lambda$, neither model alone is able to quantitatively reproduce the full data set. However considering only the points where $H<H^*$ (respectively $H>H^*$), the Darcy (resp. Poiseuille) model fits the data well albeit with a prefactor. Note that it would be easy to miss out on the failure of the Poiseuille model at small wavelengths by adding an unexplained offset \seb{(dashed line in Fig.~\ref{fig:DarcyPoiseuille}b)}. Nonetheless, a complete model (derived in Supplementary Methods), summing up the influence of both Poiseuille and Darcy dissipation shows a better agreement for all values of $H/H^*$.

>>>>

Longitudinally constrained swelling of the gel film is the origin and driving force of the buckling instability. The gel area becomes in excess compared to the available area, thus the gel must fold. However, this does not explains how a wavelength is selected.

@@

% Pour Mathieu : ajouter quelque part des applications numériques pour les trois longueurs d'ondes gravité, Darcy, Poiseuille
We identify three possible candidates for the transverse load $\sigma_\perp$: the weight or buoyancy of the gel, the porous flow through the gel or the viscous flows in the surrounding water layers. We confirmed that the former plays no significant role by successfully repeating our experiment in a cell held vertically, i.e. with the weight acting longitudinally rather than transversely.
%Since the gel is almost buoyant with the surrounding medium, we expect that the weight plays no significant role, with an elasto-gravitational length at least centimetric. We confirmed this insight by successfully repeating our experiment in a cell held vertically, i.e. with the weight acting longitudinally rather than transversely.

@@

To sum up, we expect two regimes of viscosity-dominated wrinkling: for $H\ll H^*$ the main dissipation mechanism would be the flow through the porous film, whereas for $H\gg H^*$ the flow in the viscous layers would dominate at set the wavelength.

@@

Our results are displayed in Fig.~\ref{fig:DarcyPoiseuille}. Although they provide the correct order of magnitude for $\lambda$, neither model alone is able to quantitatively reproduce the full data set. However considering only the points where $H<H^*$ (respectively $H>H^*$), the Darcy (resp. Poiseuille) model fits the data well albeit with a prefactor. Note that it would be easy to miss out on the failure of the Poiseuille model at small wavelengths by adding an unexplained offset (dashed line in Fig.~\ref{fig:DarcyPoiseuille}b). Nonetheless, a complete model (derived in Supplementary Methods), summing up the influence of both Poiseuille and Darcy dissipation shows a better agreement for all values of $H/H^*$.
